Quantifying unmet ICU beds in tertiary hospitals in urban India using Prospective Score Matching 

### 2022-09-20 manuscript.Rmd
morgonen 20/9 version för kommentering

NOTE2SELF: för projektredogörelsen feta ut och ha med paragraferna här som temporaries och säg till när de är klara för kommentering intro och metoddelen, 
Fråga Johanna: 3-5 sidor ja men det är en rekommendation och formatet med omfattande bakgrund passar inte den här typen av studie. jag kan men jag vet inte om det är meningsfullt att producera 2 sidor text baraföratt? I instruktionen skriver KI själva att det är en kontrollmekanism bara "koordinatorn får en uppfattning om progress i projektet,". Kan jag bara motivera utformningen så är jag inte orolig
<!-- Explain the scientific background and rationale for the
investigation being reported. End by stating the aim or specific
objectives, including any prespecified hypotheses. The introduction
should not be longer than 1-1.5 pages, typically 4-5 paragraphs, each
6-8 lines long. Support every statement with a citation -->

@@

Existing TQIP often originate in high-income countries, and are either not applicable nor easily transferred to the hospital conditions of low and middle income countries (LMIC). This study aims to make an TQIP assessment in an Indian context to fill part of that knowledge gap, and to test whether there is merit in the testimony of the Indian colleagues. The study shall propose a scope of the unmet need for ICU beds for trauma patients at tertiary hospitals in urban India. If this analysis indeed indicate a shortage, it can be used to motivate extending ICU resources and reduce preventable trauma morbidity and mortality.

@@

The theory being examined in this thesis is that there exist subset of the TITCO-I dataset that didn't go to the ICU, but are very similar to the patients that did go to the ICU, in the covariates that caused ICU-treated patients to receive this intervention. The thesis is that these patients were not admitted to the IC for lack of such resources. These patients will be identified using propensity score matching.

@@

KOPPAT tills jag förstår och kan omformulera
Injury descriptors and codes
A random selection of 1% of injury descriptors entered into each of the variables e_1, e_2, e_3, e_4, e_5, e_6, e_7, e_8, e_9, e_10, e_11, e_12, xray_1, xray_2, xray_3, xray_4, xray_5, xray_6, xray_7, xray_8, xray_9, xray_10, xray_11, fast_1, fast_2, fast_3, fast_4, fast_5, fast_6, fast_7, fast_8, fast_9, fast_10, fast_11, ct_1, ct_2, ct_3, ct_4, ct_5, ct_6, ct_7, ct_8, ct_9, ct_10, ct_11, ct_12, ct_13, op_1, op_2, op_3, op_4, op_5, op_6, op_7, op_8, op_9, op_10, op_11 were set to missing. Corresponding ICD-10 codes were also set to missing. This was done to prevent identification of patients based on the list of recorded injuries.
KOPPAT

@@

P-values and T-values of non-ICU vs ICU patients:

TASK4SELF: släng upp alla variabler i google sheetset
.r fil för missing cleaning av titcodatasetet
onsdag kolla kommentarerna löpande. 
kolla på textbaserade parametrar
släng upp alla tasks i slack, och instruera martin och johanna att kommentera i slack
```{r}
setwd("C:/Users/maria/Downloads/Packt Learning RStudio for R Statistical Computing 2012 RETAIL eBook-repackb00k/unmet-ICU-beds")
load("statresult.rdata")

>>>>

NOTE2SELF: för projektredogörelsen feta ut och ha med paragraferna här som temporaries och säg till när de är klara för kommentering intro och metoddelen, 
Fråga Johanna: 3-5 sidor ja men det är en rekommendation och formatet med omfattande bakgrund passar inte den här typen av studie. jag kan men jag vet inte om det är meningsfullt att producera 2 sidor text baraföratt? I instruktionen skriver KI själva att det är en kontrollmekanism bara "koordinatorn får en uppfattning om progress i projektet,". Kan jag bara motivera utformningen så är jag inte orolig jag la frågan till kursadmin
<!-- Explain the scientific background and rationale for the
investigation being reported. End by stating the aim or specific
objectives, including any prespecified hypotheses. The introduction
should not be longer than 1-1.5 pages, typically 4-5 paragraphs, each
6-8 lines long. Support every statement with a citation -->

@@

Existing TQIP often originate in high-income countries (HIC), and are either not applicable nor easily transferred to the hospital conditions of low and middle income countries (LMIC) @frailty @gunshots  @onemilliondead. Applying TQIPs outside of their original context or even within a subset of it's own origin is difficult even without taking income bracket in account, for instance firearm violence is a considerable bigger portion of trauma patients in some US contexts, than the national average @gunshot. For trauma patients, there exist significant structural differences between HIC and LMIC mainly regarding injury mechanisms and severity, health care resources as well as patient make-up @frailty @indiantrauma @traumaLMIC @onemilliondead. These differences make a direct transferral of HIC TQIP models onto LMIC irrelevant or misleading and there is a need to develop TQIP assessment applicable to local conditions. This study aims to make an TQIP assessment in an Indian context to fill part of that knowledge gap, and to test whether there is merit in the testimony of the Indian colleagues. The study shall propose a scope of the unmet need for ICU beds for trauma patients at tertiary hospitals in urban India. If this analysis indeed indicate a shortage, it can be used to motivate extending ICU resources and reduce preventable trauma morbidity and mortality.

@@

The theory being examined in this masters thesis is that there exist subset of the TITCO-I dataset that didn't go to the ICU, but are very similar to the patients that did go to the ICU, in the covariates that caused ICU-treated patients to receive this intervention. The thesis is that these patients were not admitted to the IC for lack of such resources. These patients will be identified using propensity score matching.

@@

Text based input
1% of the text-based inputs in ICD code fields and examination or operation findings were randomly deleted to obstruct identification by this variable.

@@

P-values and T-values of non-ICU vs ICU patients:
```{r}
setwd("C:/Users/maria/Downloads/Packt Learning RStudio for R Statistical Computing 2012 RETAIL eBook-repackb00k/unmet-ICU-beds")
load("statresult.rdata")
